Wigglyhedra

### 2025-01-08 draft/wigglyhedra.tex
Minor edits.

% We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
We begin by describing the category of interest, which is the bounded homotopy category of finitely-generated graded projective modules over a certain finite-dimensional algebra \(A_m\). 
It is a full subcategory of \(D^b(A_m\text{-grmod})\), the bounded derived category of finitely generated graded \(A_m\)-modules.
The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
Let~\(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
A longer path, which is a composition of arrows, will be denoted by~\((i_1, i_2, \dots, i_n)\).

@@

\begin{definition}
The category \(\mathcal{C}_m\) is defined to be the homotopy category of bounded complexes of finitely-generated graded projective \(A_m\)-modules.
\end{definition}
Note that there is an embedding of \(A_m\text{-grmod}\) into \(D^b(A_m\text{-grmod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-grmod})\).
\(\mathcal{C}_m\) is thus the smallest full triangulated subcategory of \(D^b(A_m\text{-grmod})\) containing all the objects \(P_i\langle j \rangle\).

@@

\begin{proposition}\label{prop:extensions}
For \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\), \(Y\), \(Y'\) as just discussed,
\begin{itemize}
\item if \(\alpha\) and \(\alpha'\) are not pointed, then for some \(g\) and \(g'\), we have extensions
  \[0 \to X' \to Y \to X\langle g \rangle[-g] \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X'\langle g' \rangle[-g'] \to 0;\]
\item if \(\alpha\) and \(\alpha'\) are crossing, then for some \(g\), we have an extension
  \[0 \to X' \to (Y \oplus Y') \to X\langle g \rangle[-g]\to 0.\]
\end{itemize}
\end{proposition}

>>>>

% We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
We begin by describing the category of interest, which is the bounded homotopy category of finitely-generated graded projective modules over a finite-dimensional algebra \(A_m\). 
The algebra~\(A_m\), called the \defn{zigzag algebra}, is a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
Let~\(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
A longer path, which is a composition of arrows, will be denoted by~\((i_1, i_2, \dots, i_n)\).

@@

\begin{definition}
The category \(\mathcal{C}_m\) is defined to be the homotopy category of bounded complexes of finitely-generated graded projective \(A_m\)-modules.
\end{definition}
Let \(D^b(A_m\text{-grmod})\) denote the bounded derived category of graded \(A_m\)-modules.
Note that there is an embedding of \(A_m\text{-grmod}\) into \(D^b(A_m\text{-grmod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-grmod})\).
\(\mathcal{C}_m\) is thus the smallest full triangulated subcategory of \(D^b(A_m\text{-grmod})\) containing all the objects \(P_i\langle j \rangle\).

@@

\begin{proposition}\label{prop:extensions}
For \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\), \(Y\), \(Y'\) as just discussed,
\begin{itemize}
\item if \(\alpha\) and \(\alpha'\) are not pointed, then for some integers \(g\) and \(g'\), we have extensions
  \[0 \to X' \to Y \to X\langle g \rangle[-g] \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X'\langle g' \rangle[-g'] \to 0;\]
\item if \(\alpha\) and \(\alpha'\) are crossing, then for some integer \(g\), we have an extension
  \[0 \to X' \to (Y \oplus Y') \to X\langle g \rangle[-g]\to 0.\]
\end{itemize}
\end{proposition}
